\subsection{Getting Started}

\subsubsection{HTML}
The first thing you need to do to become a Web Business entrepreneur is learn some basic HTML.  For this you will need a text editor that can write plain ascii files...i.e. NOT MS WORD.  Notepad will do, but it sucks ass.  Just find a simple text editor initially, but also consider mastering a more powerful editor.  My personal recommendation would be either Eclipse or Emacs.  Eclipse might be easier to learn because it is very visual.  If you want to get very hard core like me...go for Emacs.  Regardless, your first steps will be to learn some basic HTML.  I'm not going to reproduce HTML tutorials here, as they abound on the web, so go to google and learn some.  However, I'll say some topics that you should understand.

\begin{itemize}
\item Try to understand how to create a table in HTML.
\item Know how to include an image, a hyperlink, even a video.
\item Learn how to do basic formatting, like font size, bold, etc...
\end{itemize}

That should get you started for HTML.  Now lets move onto CSS.

\subsubsection{CSS}

You need to learn the basics of CSS.  Here are the bullet point topics to understand:

\begin{itemize}
\item Learn how to include an external CSS file in your HTML file you created above.
\item Learn how to control font size and color in your CSS.
\end{itemize}

Again, I won't go into how to do that here, as tutorials abound on the web.

\subsubsection{Javascript}

Once you start learning Javascript, you are getting quite advanced.  Here is a short list of
items/objectives you can aim to become able to do.

\begin{itemize}
\item Check that the value of a text input box is a number
\item Mousing over an image updates the value of some text somewhere in the DOM (Document Object Model)
\end{itemize}

I recommend you use firebug, a firefox plugin, that allows you to debug
javascript.

\subsection{Conclusion}

If you can learn the above items, you have progressed quite far in your education of Web technologies.  All of the above is what we call 'client-side' technologies.  There are 'server-side' technologies.  Common types of these are PHP, Perl-CGI, Ruby on Rails, JSP's, ASP's, etc...







%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "OnlineTailorStrategyBook"
%%% End: 
